The Unicode Cookbook \linebreak for Linguists

### 2018-06-19 book/chapters/implementation.tex
various fixes

Besides the columns \texttt{Left}, \texttt{Grapheme}, and \texttt{Right} as
discussed in the previous sections, there are also columns \texttt{Class} and
\texttt{Replacement}. The column \texttt{Class} can be used to specify classes
of graphemes that can then be used in the contextual specification. The column
\texttt{Replacement} is just a copy of the column \textt{Grapheme}, providing a
skeleton to specify transliteration. The name of the column
\texttt{Replacement} is not fixed -- there can actually be multiple columns with 
different kinds of transliterations in a single profile.

@@

The two recipes using the Python \textt{segments} package include a tutorial on how to segment graphemes in IPA text:

>>>>

Besides the columns \texttt{Left}, \texttt{Grapheme}, and \texttt{Right} as
discussed in the previous sections, there are also columns \texttt{Class} and
\texttt{Replacement}. The column \texttt{Class} can be used to specify classes
of graphemes that can then be used in the contextual specification. The column
\texttt{Replacement} is just a copy of the column \texttt{Grapheme}, providing a
skeleton to specify transliteration. The name of the column
\texttt{Replacement} is not fixed -- there can actually be multiple columns with 
different kinds of transliterations in a single profile.

@@

The two recipes using the Python \texttt{segments} package include a tutorial on how to segment graphemes in IPA text:
